

In this file, we prove the Prime Number Theorem. Continuations of this project aim to extend
this work to primes in progressions (Dirichlet's theorem), Chebytarev's density theorem, etc
etc.




A function is Meromorphic on a rectangle with corners $z$ and $w$ if it is holomorphic off a
(finite) set of poles, none of which are on the boundary of the rectangle.



Discuss polar behavior of meromorphic functions

A




We show that if a function is meromorphic on a rectangle, then the rectangle integral of the
function is equal to the sum of the residues of the function at its poles.



MellinTransform

Mellin Inversion (Goldfeld-Kontorovich)

ChebyshevPsi

ZeroFreeRegion

Hadamard Factorization

Hoffstein-Lockhart + Goldfeld-Hoffstein-Liemann

LSeries (NatPos->C)

RiemannZetaFunction

RectangleIntegral

ResidueTheoremOnRectangle

ArgumentPrincipleOnRectangle

Break rectangle into lots of little rectangles where f is holomorphic, and squares with center at a pole

HasPoleAt f z : TendsTo 1/f (N 0)

Equiv: TendsTo f atTop

Then locally f looks like (z-z_0)^N g

For all c sufficiently small, integral over big rectangle with finitely many poles is equal to rectangle integral localized at each pole.
Rectangles tile rectangles! (But not circles -> circles) No need for toy contours!




\begin{definition}
The Chebyshev Psi function is defined as
$$
\psi(x) = \sum_{n \leq x} \Lambda(n),
$$
where $\Lambda(n)$ is the von Mangoldt function.
\end{definition}




Main Theorem: The Prime Number Theorem
\begin{theorem}[PrimeNumberTheorem]
$$
ψ (x) = x + O(x e^{-c \sqrt{\log x}})
$$
as $x\to \infty$.
\end{theorem}


